Appendix B: R Functions for Design Analysis Pearson Correlation

### 2020-04-28 Documents/Appendix_B/Appendix_B.Rmd
Appendix B update

For further details run the line `docstring(retro_r)` or `docstring(pro_r)`. This creates a documentation similar to the help pages for R functions.

>>>>

For further details about function arguments, run the line `docstring(retro_r)` or `docstring(pro_r)`. This creates a documentation similar to the help pages of R functions.
